---
title: "Data filtering"
author: "Kamile Jurgaitiene"
date: "2023-04-27"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Preparation 
Uploading CSV file to R and skipping not needed line.

```{r cars}
setwd("/Users/kamilejurgaitiene/Downloads")
getwd()
library(readr)
AmazonQ1 <- read_csv("AmazonQ1.csv", skip=1)
View(AmazonQ1)
head(AmazonQ1) #data summary
colnames(AmazonQ1) #column names
```

#Delete not needed data

```{r cars}
library(dplyr)
AmazonQ1 <- select(AmazonQ1,-"Top Clicked Product #1: Product Title", -"Top Clicked Product #2: Product Title", -"Top Clicked Product #3: Product Title")
```

#Categories filter 
We prepare and separate top clicked categories columns (-\> categories) and we combine all Categories we want to
exclude (-\> delcategories).

The 'for' loops are used to loop over each column and keyword
combination, and the 'grepl()' function is used to check if each keyword
is present in each column.

```{r cars}
categories <- c("Top Clicked Category #1", "Top Clicked Category #2", "Top Clicked Category #3" )
delcategories <- c("Amazon_Prints","Mobile_Apps", "Apparel", "Video Games", "Software", "Grocery", "Audible", "Books","Digital_Video_Download", "Gift Card", "Furniture", "Shoes", "Art and Craft Supplies", "Prescription_Drugs", "Digital_Music_Purchase", "Sports Memorabilia", "Tires", "Jewelry", "Digital_Video_Games")

for (col in categories) {for (kw in delcategories) {AmazonQ1 <- AmazonQ1[!grepl(kw, AmazonQ1[[col]], ignore.case = TRUE),]}}
```

#Brands filter 
We prepare and separate top Brands (-\> brands) and we combine all brands we want to exclude (-\> delbrands).

The 'for' loops are used to loop over each column and keyword
combination, and the 'grepl()' function is used to check if each keyword
is present in each column.

```{r cars}
brands <- c("Top Clicked Brand #1", "Top Clicked Brands #2", "Top Clicked Brands #3" )
delbrands <- c("Apple", "Lenovo", "HP", "beats", "JBL", "Samsung", "BRITA
", "CeraVe", "Cetaphil", "SanDisk", "Milwaukee", "LEGO", "Sony", "Dove", "Hallmark", "Pokemon", "Maybelline", "L'OREAL PARIS", "Air Wick", "KitchenAid", "Nivea", "NIKE", "Garnier", "Pampers", "Fisher-price", "Energizer", "DURACELL", "KODAK", "COVERGIRL", "Canon", "REVLON", "CRAYOLA")

for (col in brands) {for (kw in delbrands) {AmazonQ1 <- AmazonQ1[!grepl(kw, AmazonQ1[[col]], ignore.case = TRUE),]}}
```

#Search terms filter 
We prepare column 'search terms' (-\> terms) and we combine all search term we want to excluede (-\> delterms).

The 'for' loops are used to loop over each column and keyword
combination, and the 'grepl()' function is used to check if each keyword
is present in each column.

```{r cars}
terms <- c("Search Term")
delterms <- c("Lenovo", "HP", "beats", "JBL", "Samsung", "BRITA", "CeraVe", "Cetaphil", "SanDisk", "Milwaukee", "Pokemon", "iphone", "1", "alexa", "kindle", "led lights", "squishmallow", "water bottles", "valentines day gifts", "mouse pad", "valentines cards", "scrub daddy", "valentines day decor","hello kitty", "ipad", "fitbit", "sol de janeiro", "desk organizers and accessories", "airpod pro case", "Shampoo", "Tylenol", "lotion", "lashes", "tattoo", "handsoap", "decor", "stickers", "Disney", "nail polish", "paint", "perfume", "sex", "supplement")

for (col in terms) {for (kw in delterms) {AmazonQ1 <- AmazonQ1[!grepl(kw, AmazonQ1[[col]], ignore.case = TRUE),]}}
```

#Search terms finder 

If we want to find certain search terms just change word "japanese knife" to any of the interest.

```{r cars}
matches <- apply(AmazonQ1, 1, function(x) any(grepl("japanese knife", x)))
AmazonQ1[matches, ]
View(AmazonQ1[matches, ])
```

#Select certain range 
If we want to select certain range of date in terms of SFR and Top clicked click share.

```{r cars}
#SFR
Orbio <-AmazonQ1[AmazonQ1$`Search Frequency Rank` >= 2000 & AmazonQ1$`Search Frequency Rank` <= 100000, ]
View(Orbio)

#Top clicked click share
Orbio[Orbio$`Top Clicked Product #1: Click Share` >= 9 & Orbio$`Top Clicked Product #1: Click Share` <= 100, ]
View(Orbio)
```

#export file

```{r cars}
write.csv(AmazonQ1, "output_AMZQ1.csv", row.names = FALSE)
```
